The five pillars of computational reproducibility: Bioinformatics and beyond

### 2023-06-10 manuscript/5pillars.Rmd
Add warning about non-moderated data repositories

High throughput biology has already built a number of data repositories for specific data types
conforming to FAIR principles (e.g.: GEO, SRA, ENA, PRIDE [@Edgar2002-hs; @Kodama2012-bn; @Deutsch2017-hc]).
However other domains lack well known specialized organized data repositories, such as evolutionary
biology, ecology, cell biology, social sciences and computing.
The [re3data.org](https://www.re3data.org/) registry of data repositories may be useful to find a
repository that accepts data from these fields [@Pampel2013-ep].
If no specialized repository exists, then a general-purpose repository such as
[Dryad](https://datadryad.org/), [FigShare](https://figshare.com/), or [Zenodo](https://zenodo.org/)
should be considered.
Moreover, general recommendations have been proposed to enhance data FAIRness in ecology, but which
can also be applied to other disciplines [@Roche2015-aq].

>>>>

High throughput biology has already built a number of data repositories for specific data types
conforming to FAIR principles (e.g.: GEO, SRA, ENA, PRIDE [@Edgar2002-hs; @Kodama2012-bn; @Deutsch2017-hc]).
However other domains lack well known specialized organized data repositories, such as evolutionary
biology, ecology, cell biology, molecular simulation, social sciences and computing.
The [re3data.org](https://www.re3data.org/) registry of data repositories may be useful to find a
repository that accepts data from these fields [@Pampel2013-ep].
If no specialized repository exists, then a general-purpose repository such as
[Dryad](https://datadryad.org/), [FigShare](https://figshare.com/), or [Zenodo](https://zenodo.org/)
should be considered. Researchers should be aware, however, that these repositories are often not moderated, 
and that it is their responsibility to make their data FAIR, in particular by providing sufficient metadata.
To this aime, general recommendations have been proposed to enhance data FAIRness in ecology, but which
can also be applied to other disciplines [@Roche2015-aq].
